%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemPlain}[2]{
  \item\small{
    \textbf{#1}{#2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://www.linkedin.com/in/ankith-rd/}{\Large Ankith Divakar Raja}} & Email : \href{mailto:araja2@ncsu.edu}{araja2@ncsu.edu}\\
  \href{https://www.linkedin.com/in/ankith-rd/}{https://www.linkedin.com/in/ankith-rd/} & Mobile : 919-946-6195 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {North Carolina State University}{Raleigh, NC}
      {Master of Science in Computer Networking;  GPA: 3.9 / 4.0}{}
    \quad \item \textit{\textbf{Relavent Coursework:} Object Oriented Development, Operating System, Algorithms, SDN, Java J2EE, Data Structures, DBMS}  
      
    \resumeSubheading
      {R V College of Engineering}{Bangalore, India}
      {Bachelor of Engineering in Telecommunication;  GPA: 4.0 / 4.0 }{Sept 2010 -- May 2014}
  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Technical Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Languages}
      {Java, Python, Ruby, C++, MySQL, C}
    \resumeSubItem{Frameworks}
      {Spring, Strut2, Hibernate, Ruby on Rails, JDBC }  
    \resumeSubItem{Platforms}
      {Windows, Linux, AWS, Heroku, Android }
    \resumeSubItem{Tools}
      {Mule ESB, SonarQube, J-Unit, J-Meter, Jenkins, DexGuard, Apache Maven, SVN, Git }
%    \resumeSubItem{Others}
%      {Socket Prgramming, TCP/IP, Routing Protocols, Agile Medhodologies}
  \resumeSubHeadingListEnd



%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Mahindra Comviva Ltd}{Bangalore, India}
      {Senior Software Engineer}{June 2016 - July 2017}
      \resumeItemListStart
        \resumeItem{Host Card Emulation}
          {Designed the application architecture for payments using HCE. Worked with senior software architect to complete the design, which focused on providing modularity, security and scalability.}
        \resumeItemPlain{}
          {Developed the \textbf{Proof of Concept} to generate and store \textbf{digital receipt} for transactions performed using HCE. Integrated the receipt module with \textbf{Android application} to display the digital receipt. Client: Serco}
        \resumeItemPlain{}
          {Obfuscated code using \textbf{DexGuard} command line tool for HCE SDK to \textbf{secure} against reverse engineering of APIs. Worked directly with the DexGuard Software team to achieve 100 percent \textbf{code obfuscation}.}
        \resumeItemPlain{}
          {\textbf{Integrated} existing Kotak bank \textbf{KYC verification, NEFT and IMPS payment} services with digital wallet making the services accessible through \textbf{REST APIs}.}  
      \resumeItemListEnd
      
    \resumeSubheading
      {Mahindra Comviva Ltd}{Bangalore, India}
      {Software Engineer}{Sept 2014 - June 2016}
      \resumeItemListStart
        \resumeItemPlain{}
          {Developed \textbf{SOAP/XML APIs} for \textbf{digital wallet application} based on \textbf{Mule ESB} for features like addition, deletion of Card, online payment using bank account/card. Involved extensively working with java frameworks like \textbf{Spring, Struts and Hibernate}.}
        \resumeItemPlain{}
          {\textbf{Migrated} digital wallet application APIs developed based on \textbf{SOAP/XML to REST/JSON} using GSON library. Application \textbf{performance improved} by 30 percent.}
        \resumeItemPlain{}
          {Worked on \textbf{Proof of Concept} with MTS Russia application team using \textbf{Agile scrum methodology} to develop feature for \textbf{interoperability} of multiple digital wallets using Mule ESB. Developed \textbf{Java REST APIs} to make \textbf{dynamic payments} using multiple wallets.}
        \resumeItemPlain{}
          {\textbf{Refactored code} for Mobiquity money banking software using \textbf{SonarQube Code Climate}, reduced the code base by 45 percent and \textbf{application performance increased} by 28 percent.}
        
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Peer2Peer File Transfer}
      {Self Synchronized P2P file transfer system with distributed file index was developed using \textbf{Python3} multithreading. Linked List data-structure was used to store peer and file information.}
    \resumeSubItem{Expertiza(Open Source)}
      {Contributed to open source Expertiza project by developing a timeline feature to visualize the submissions against due dates and deadlines, for students to keep track of the project progress and deadlines. \textbf{Tools: Ruby on Rails, HTML5, BootStrap, CSS3}}
    \resumeSubItem{Wireshark(Open Source)}
      {Working with open source wireshark project team to design a dissector in \textbf{C} to analyze data packets containing Constrained Application Protocol for Patch, iPatch and Fetch methods in RFC 8132.}
    \resumeSubItem{Point to Multi Point Reliable Transfer}
      {Virtualized point to point reliable connection to provide point to multipoint reliable connection for simultaneous file transfer to all peers. Developed using \textbf{Python3} multithreading functionality.}
    \resumeSubItem{Web Application}
      {Designed and deployed car rental application on \textbf{heroku}, which provided easy booking and checkout functionality in multiple locations. It was designed to provide dynamic pricing based on the time duration. \textbf{Tools: Ruby on Rails, HTML5, BootStrap, CSS3}}
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
